### 2025-02-28 paper/sections/ExperimentalSetup.tex
add task paper citation

This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, computational resources, and the tools and libraries utilized. The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.
\begin{figure*}[t]
    \centering
    \includegraphics[width=1.7\columnwidth]{images/confusion_matrices_all_tracks.png}
    \caption{Confusion matrices for each language across Tracks A, B, and C.}
    \label{fig:confusion_matrices}
\end{figure*}

>>>>

This section outlines the experimental setup, including data splits, preprocessing, hyperparameter tuning, computational resources, and the tools and libraries used, aiming for reproducibility and transparency.
All experiments and evaluation protocols in this work are conducted following the guidelines specified in SemEval-2025 Task 11 \cite{muhammad-etal-2025-semeval}, which establishes the framework for text-based emotion detection.

\begin{figure*}[t]
    \centering
    \includegraphics[width=1.7\columnwidth]{images/confusion_matrices_all_tracks.png}
    \caption{Confusion matrices for each language across Tracks A, B, and C.}
    \label{fig:confusion_matrices}
\end{figure*}
